Proof of Identity

### 2022-06-26 paper.tex
Update paper.tex
none
K_id, K_p instead of K, P; explanations; notation

\newcommand{\khk}{$P$}
\newcommand{\khkp}{$K^{-1}[\text{HK}]$}
\newcommand{\identity}{\textit{Identity}}
%\newcommand{\kid}{$K[\text{\identity}]$}
\newcommand{\kid}{$K$}
\newcommand{\todo}[1]{\fbox{\parbox{\linewidth}{\textcolor{red}{#1}}}}
\newcommand{\iv}{$IV(\text{\identity})$}
\newcommand{\sigid}{$K^{-1}[CA](K[Identity])$}
\newtheorem{problem}{Problem}
\newenvironment{solution}
  {\emph{Solution:}}
  {\hfill $\square$}
\newcommand{\pbc}{\textit{PeopleBC}}

\title{Proof of Identity}
\author{Albert Vučinović, University North}
\begin{document}
\maketitle
\section{Notation}
\begin{tabular}{p{0.36\linewidth}|p{0.55\linewidth}}
	\kid &  State CA certified public key of e.g. eID\\
	$K(value)$ & $value$ encrypted with the public key $K$. \\
	$\kid^{-1}$ & Private key corresponding to the public key $K$. \\
  \khk & Person key, used to access PeopleBC as an unknown Person. \\
  $H$ & SHA256 \\
\end{tabular}

\newpage
\section{Registering \khk{} (Person key)}
\begin{enumerate}
  \item Use \kid{} to sign "PeopleBC", $K_1 = \kid^{-1}("registerK")$.
  \begin{enumerate}
    \item Entities who know \kid{} (e.g. CA that issued it) can know that the Person is using PeopleBC, and what identification document the Person is using.
  \end{enumerate}
  \item Register \kid{} on \pbc, by calling 
    $$registerK(Pin, K_1, proofPinOwnsK)$$.
  \item Register \khk{} on \pbc, by calling 
    $$registerP(PinK, PinKP, proof)$$
  where:
    \begin{enumerate}
      \item $K_2=\kid^{-1}("registerP")$
      \item $PinK=H(Pin,K_2)$
      \item $P_1 = \khk^{-1}("registerP")$
      \item $PinKP=H(Pin, K_2, P_1)$
    \end{enumerate}
\end{enumerate}

>>>>

\newcommand{\khk}{K_{P}}
\newcommand{\khkp}{$K^{-1}[\text{HK}]$}
\newcommand{\kid}{K_{ID}}
%\newcommand{\kid}{$K$}
\newcommand{\todo}[1]{\fbox{\parbox{\linewidth}{\textcolor{red}{#1}}}}
\newcommand{\iv}{$IV(\text{\identity})$}
\newcommand{\sigid}{$K^{-1}[CA](K[Identity])$}
\newtheorem{problem}{Problem}
\newenvironment{solution}
  {\emph{Solution:}}
  {\hfill $\square$}
\newcommand{\pbc}{\textit{Identity Blockchain}}

\title{Proof of Identity}
\author{
Albert Vučinović, University North\\
Miroslav Jerković, University of Zagreb
}
\begin{document}
\maketitle
\section{Notation}
\begin{tabular}{p{0.36\linewidth}|p{0.55\linewidth}}
  $(K, K^{-1})$ & A pair of public $K$ and the corresponding private key $K^{-1}$. \\
	$K(value)$ & $value$ encrypted with a public key $K$. \\
	$K^{-1}(value)$ & $value$ encrypted with a private key $K^{-1}$. \\
  $H$ & Hash function, e.g. some zksnark friedly one \\
	$\kid$ &  State CA certified public key of e.g. eID\\
  $\khk$ & Person key, public key used to access \pbc{} as an unknown Person. \\
  $Nin$ & A personal National Identification Number issued by state.
\end{tabular}

Sometimes we write $K$ for $(K, K^{-1})$.

\newpage
\section{Registering $\khk$ (Person key)}
\begin{enumerate}
  \item Register $\kid$ on \pbc, by calling 
    $$register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK).$$

    The Person tells the \pbc{} what personal identification document will they be using.

    What is the meaning behind $register\kid$ function?
    \begin{itemize}
      \item Sybil resistance. To prevent a Person from registering more than one $\khk$ using different identification documents, which are issued for the same $Nin$.
      \item Loss of $\kid$. If a Person looses previously registered $\kid$ (e.g. by loosing the eID), they can register a new one.
      \item Identity theft damage control. If a Person overwrites the previous $\kid$ with a new one, the identity thief will loose access to services that check the whole identity chain.
    \end{itemize}

    Entities who know $\kid$ (e.g. CA that issued it) can know that the Person is using \pbc{}, and what identification document the Person is using.

  \item Register $\khk$ on \pbc, by calling 
    $$register\khk(Nin\kid, Nin\kid\khk, proof)$$
  where:
    \begin{enumerate}
      \item $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$
    \end{enumerate}
\end{enumerate}
